Under-approximation of reachability through static analysis in multivalued asynchronous networks

### 2013-03-31 parts/sa.tex
conclusion
example

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \label{fig:sa-livelock}
  \caption{
    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
    \pref{th:approxinf} is inconclusive on this example as the only solution of process $ab_{11}$ is not coherent (\pref{def:coherent}).
  }
\end{figure}

>>>>

\begin{example}
  As an example showing the usefulness of our method, we can consider \pref{fig:ph-livelock}.
  Let $\PH' = (\PHs, \PHl, \PHh'^{\langle 1 \rangle})$ be the “flattened” version of $\PH$, that is: $\PHh'^{\langle 1 \rangle} = \PHh^{(1)} \cup \PHh^{(2)}$.
  As this PH model contains only $1$ priority, it is equivalent to a PH in the semantics without priorities.
  The under-approximation on this class of models developed in~\cite{PMR12-MSCS} concludes that $c_1$ is reachable.
  This is due to the “temporal shift” inherent to cooperative sorts in the semantics without priorities.

  This is an unwanted behaviour that the semantics of PH with priorities proposed in this paper allows to avoid.
  Indeed, the under-approximation given in \pref{th:approxinf} does not conclude as one of the edges of the resulting graph of local causality is not coherent (\pref{def:coherent}).
  The graph of local causality for this example is given in \pref{fig:sa-livelock}.
\end{example}

@@

    (b0) edge (b10) edge (b00)
    (b10) edge (b10s)
    (b00) edge (b00s)
    (b1) edge (b01) edge (b11)
    (b01) edge (b01s)
    (b01s) edge (a0)
    (b11) edge (b11s)
    ;
    \end{tikzpicture}
  \caption{
  \label{fig:sa-livelock}
    The graph of local causality of the PH model in \pref{fig:ph-livelock}.
    \pref{th:approxinf} is inconclusive on this example as the only solution of process $ab_{11}$ is not coherent (\pref{def:coherent}).
  }
\end{figure}

\todo{La méthode permet aussi de conclure sur l'accessilibité d'un état (global ou partiel)}
